\makeatletter
\newcommand{\checkForEnd}{\@ifnextchar\uppercase{}{\item}}
\makeatother
\newenvironment{foo}
{\par\obeylines
\begingroup\lccode`~=`\^^M
\lowercase{\endgroup\let~}\checkForEnd
\begin{enumerate}}
{\end{enumerate}}


\begin{foo}
The city councilmen refused the demonstrators a permit because they [feared/advocated] violence. Who [feared/advocated] violence? Answers: The city councilmen/the demonstrators.
The trophy doesn't fit into the brown suitcase because it's too [small/large]. What is too [small/large]? Answers:The suitcase/the trophy.
Joan made sure to thank Susan for all the help she had [given/received]. Who had [given/received] help? Answers: Susan/Joan.
Paul tried to call George on the phone, but he wasn't [successful/available]. Who was not [successful/available]? Answers: Paul/George
The lawyer asked the witness a question, but he was reluctant to [answer/repeat] it. Who was reluctant to [answer/repeat] the question? Answers: The witness/the lawyer.
The delivery truck zoomed by the school bus because it was going so [fast/slow]. What was going so [fast/slow]? Answers: The truck/the bus
Frank felt [vindicated/crushed] when his longtime rival Bill revealed that he was the winner of the competition. Who was the winner of the competition? Answers: Frank/Bill
The man couldn't lift his son because he was so [weak/heavy]. Who was [weak/heavy]? Answers: The man/the son.
The large ball crashed right through the table because it was made of [steel/styrofoam]. What was made of [steel/styrofoam]? Answers: The ball/the table.
John couldn't see the stage with Billy in front of him because he is so [short/tall]. Who is so [short/tall]? Answers: John/Billy.
Tom threw his schoolbag down to Ray after he reached the [top/bottom] of the stairs. Who reached the [top/bottom] of the stairs? Answers:Tom/Ray.
Although they ran at about the same speed, Sue beat Sally because she had such a [good/bad] start. Who had a [good/bad] start? Answers: Sue/Sally.
The sculpture rolled off the shelf because it wasn't [anchored/level]. What wasn't [anchored/level]? Answers: The sculpture/the shelf.
Sam's drawing was hung just above Tina's and it did look much better with another one [below/above] it. Which looked better? Answers: Sam's drawing/Tina's drawing.
Anna did a lot [better/worse] than her good friend Lucy on the test because she had studied so hard. Who studied hard? Answers: Anna/Lucy
The firemen arrived [after/before] the police because they were coming from so far away. Who came from far away? Answers: The firemen/the police.
Frank was upset with Tom because the toaster he had [bought from/sold to] him didn't work. Who had [bought/sold] the toaster? Answers: Frank/Tom.
Jim [yelled at/comforted] Kevin because he was so upset. Who was upset?
Answer  : Jim/Kevin.The sack of potatoes had been placed [above/below] the bag of flour, so it had to be moved first. What had to be moved first? Answers: The sack of potatoes/the bag  of flour.
Pete envies Martin [because/although] he is very successful. Who is very successful? Answers: Martin/Pete. 
I was trying to balance the bottle upside down on the table, but I couldn't do it because it was so [top-heavy/uneven]. What was [top-heavy/uneven]? Answers: the bottle/the table.
I spread the cloth on the table in order to [protect/display] it. To [protect/display] what? Answers: the table/the cloth.
The older students were bullying the younger ones, so we [rescued/punished] them. Whom did we [rescue/punish]? Answers: The younger students/the older students.
I poured water from the bottle into the cup until it was [full/empty]. What was [full/empty]? Answers: The cup/the bottle.
Susan knows all about Ann's personal problems because she is [nosy/indiscreet]. Who is [nosy/indiscreet]? Answers: Susan/Anne.
Sid explained his theory to Mark but he couldn't [convince/understand] him. Who did not [convince/understand] whom? Answer Pair A: Sid did not convince Mark/Mark did  not convince Sid. Answer Pair B:  Sid did not understand Mark/Mark did not understand  Sid.
Susan knew that Ann's son had been in a car accident, [so/because] she told her about it. Who told the other about the accident? Answers: Susan/Ann.
Joe's uncle can still beat him at tennis, even though he is 30 years [older/younger]. Who is [older/younger]? Answers:Joe's uncle/Joe.
The police left the house and went into the garage, [where/after] they found the murder weapon. Where did they find the murder weapon? Answers: In the garage/in the house.
The painting in Mark's living room shows an oak tree. It is to the right of [the bookcase/a house]. What is to the right of [the bookcase/a house]? Answers: The painting/the tree.
There is a gap in the wall. You can see the garden [through/behind] it. You can see the garden [through/behind] what? Answers: The gap/the wall.
The drain is clogged with hair. It has to be [cleaned/removed]. What has to be [cleaned/removed]? Answers: The drain/the hair.
My meeting started at 4:00 and I needed to catch the train at 4:30, so there wasn't much time. Luckily, it was [short/delayed], so it worked out. What was [short/delayed]? Answers: The meeting/the train.
There is a pillar between me and the stage, and I can't [see/see around] it. What can't I [see/see around]? Answers: The stage/the pillar.
They broadcast an announcement, but a subway came into the station and I couldn't [hear/hear over] it. What couldn't I [hear/hear over]? Answers: The announcement/the subway
In the middle of the outdoor concert, the rain started falling, [and/but] it continued until 10. What continued until 10? Answers: The rain/the concert.
I used an old rag to clean the knife, and then I put it in the [drawer/trash]. What did I put in the [drawer/trash]? Answers: The knife/the rag.
Ann asked Mary what time the library closes, [but/because] she had forgotten. Who had forgotten? Answers:Mary/Ann.
I took the water bottle out of the backpack so that it would be [lighter/handy]. What would be [lighter/handy]? Answers: The backpack/the bottle.
I couldn't put the pot on the shelf because it was too [high/tall]. What was too [high/tall]? Answers: The shelf/the pot.
I'm sure that my map will show this building; it is very [famous/good]. What is [famous/good]? Answers: The building/the map.
Bob paid for Charlie's college education. He is very [generous/grateful]. Who is [generous/grateful]? Answers: Bob/Charlie.
Bob paid for Charlie's college education, but now Charlie acts as though it never happened. He is very [hurt/ungrateful]. Who is [hurt/ungrateful]? Answers: Bob/Charlie
Bob was playing cards with Adam and was way ahead. If Adam hadn't had a sudden run of good luck, he would have [won/lost]. Who would have [won/lost]? Answers: Bob/Adam.
Adam can't leave work here until Bob arrives to replace him. If Bob had left home for work on time, he would be [here/gone] by this time. Who would be [here/gone]? Answers: Bob/Adam
If the con artist has succeeded in fooling Sam, he would have [gotten/lost] a lot of money. Who would have [gotten/lost] the money? Answers: The con artist/Sam.
It was a summer afternoon, and the dog was sitting in the middle of the lawn. After a while, it got up and moved to a spot under the tree, because it was [hot/cooler]. What was [hot/cooler]? Answers: The dog/The spot  under the tree.
The cat was lying by the mouse hole waiting for the mouse, but it was too [cautious/impatient]. What was too [cautious/impatient]? Answers: The mouse/the cat.
Anne gave birth to a daughter last month. She is a very charming [woman/baby]. Who is a very charming [woman/baby]? Answers: Anne/Anne's daughter.
Alice tried frantically to stop her daughter from [chatting/barking] at the party, leaving us to wonder why she was behaving so strangely. Who was behaving strangely? Answers: Alice/Alice's daughter.
I saw Jim yelling at some guy in a military uniform with a huge red beard. I don't know [who/why] he was, but he looked very unhappy. Who looked very unhappy? Answers: The guy in the uniform/Jim.
The fish ate the worm. It was [tasty/hungry]. What was [tasty/hungry]? Answers: The worm/the  fish.
I was trying to open the lock with the key, but someone had filled the keyhole with chewing gum, and I couldn't get it [in/out]. What couldn't I get [in/out]? Answers: The key/the chewing gum.
The dog chased the cat, which ran up a tree. It waited at the [top/bottom]. Which waited at the [top/bottom]? Answers: The cat/the do g.
In the storm, the tree fell down and crashed through the roof of my house. Now, I have to get it [removed/repaired]. What has to be [removed/repaired]? Answers: The  tree/the roof.
The customer walked into the bank and stabbed one of the tellers. He was immediately taken to the [emergency room/police station]. Who was taken to the [emergency room/police station]? Answers: The teller/the customer.
John was doing research in the library when he heard a man humming and whistling. He was very [annoyed/annoying]. Who was [annoyed/annoying]? Answers:John/the hummer.
John was jogging through the park when he saw a man juggling watermelons. He was very [impressed/impressive]. Who was [impressed/impressive]? Answers: John/the juggler.
Bob collapsed on the sidewalk. Soon he saw Carl coming to help. He was very [ill/concerned]. Who was [ill/concerned]? Answers: Bob/Carl.
Sam and Amy are passionately in love, but Amy's parents are unhappy about it, because they are [snobs/fifteen]. Who are [snobs/fifteen]? Answers: Amy's parents/Sam and Amy.
Mark told Pete many lies about himself, which Pete included in his book. He should have been more [truthful/skeptical]. Who should have been more [truthful/skeptical]? Answers: Mark/Pete.
Joe has sold his house and bought a new one a few miles away. He will be moving [out of/into] it on Thursday. Which house will he be moving [out of/into]? Answers: The old house/the new house.
Many people start to read Paul's books and can't put them down. They are [gripped/popular] because Paul writes so well. Who or what are [gripped/popular]? Answers: The readers/the books.
Mary took out her flute and played one of her favorite pieces. She has [loved/had] it since she was a child. What has Mary [loved/had] since she was a child? Answers: The piece/the flute.
Sam pulled up a chair to the piano, but it was broken, so he had to [stand/sing] instead. What was broken? Answers: The chair/the piano.
Since it was raining, I carried the newspaper [over/in] my backpack to keep it dry. What was I trying to keep dry? Answers: The backpack /the newspaper.
Sara borrowed the book from the library because she needs it for an article she is working on. She [reads/writes] it when she gets home from work. What does Sara [read/write] when she gets home from work? Answers: The book/the article.
This morning, Joey built a sand castle on the beach, and put a toy flag in the highest tower, but this afternoon [a breeze/the tide] knocked it down. What did the [breeze/tide] knock down? Answers: The  flag/the sand castle.
Jane knocked on Susan's door, but there was no answer. She was [out/disappointed]. Who was [out/disappointed]? Answers: Susan/Jane.
Jane knocked on the door, and Susan answered it. She invited her to come [out/in]. Who invited whom? Answers: Jane invited Susan an/Susan invited Jane.
Sam took French classes from Adam, because he was [eager/known] to speak it fluently. Who was [eager/known] to speak French fluently? Answers: Sam/Adam.
The path to the lake was blocked, so we couldn't [reach/use] it. What couldn't we [reach/use]? Answers: The lake/the path.
The sun was covered by a thick cloud all morning, but luckily, by the time the picnic started, it was [gone/out]. What was [gone/out]? Answers: The cloud/the sun.
We went to the lake, because a shark had been seen at the ocean beach, so it was a [dangerous/safer] place to swim. Which was a [dangerous/safer] place to swim? Answers: The beach/t he lake.
Sam tried to paint a picture of shepherds with sheep, but they ended up looking more like [dogs/golfers]. What looked like [dogs/golfers]? Answers:the sheep/the shepherds.
Mary tucked her daughter Anne into bed, so that she could [sleep/work]. Who is going to [sleep/work]? Answers: Anne/Mary.
Fred and Alice had very warm down coats, but they were not [enough/prepared] for the cold in Alaska. Who or what were not [enough/prepared] for the cold? Answers: The coats/Fred and Alice.
Thomson visited Cooper's grave in 1765. At that date he had been [dead/travelling] for five years. Who had been [dead/travelling] for five years? Answers: Cooper/Thomson
Jackson was greatly influenced by Arnold, though he lived two centuries [earlier/later]. Who lived [earlier/later]? Answers: Arnold/Jackson.
Tom's daughter Eva is engaged to Dr. Stewart, who is his partner. The two [doctors/lovers] have known one another for ten years. Which two people have known one another for ten years? Answers: Tom and Dr. Stewart/Eva and Dr. Stewart.
I can't cut that tree down with that axe; it is too [thick/small]. What is too [thick/small]? Answers: The tree/the axe.
The foxes are getting in at night and attacking the chickens. I shall have to [guard/kill] them. What do I have to [guard/kill]? Answers: The chickens/the foxes.
The foxes are getting in at night and attacking the chickens. They have gotten very [bold/nervous]. What has gotten [bold/nervous]? Answers: The foxes/the chickens.
Fred covered his eyes with his hands, because the wind was blowing sand around. He [opened/lowered] them when the wind stopped. What did Fred [open/lower]? Answers: His eyes/his hands.
The actress used to be named Terpsichore, but she changed it to Tina a few years ago, because she figured it was [easier/too hard] to pronounce. Which name was [easier/too hard] to pronounce? Answers: Tina/Terpsichore.
Fred watched TV while George went out to buy groceries. After an hour he got [up/back]. Who got [up/back]? Answers: Fred/George.
Fred was supposed to run the dishwasher, but he put it off, because he wanted to watch TV. But the show turned out to be boring, so he changed his mind and turned it [on/off]. What did Fred turn [on/off]? Answers: The dishwasher/the television.
Fred is the only man still alive who remembers my great-grandfather. He [is/was] a remarkable man. Who [is/was] a remarkable man? Answers: Fred/my great-grandfather.
Fred is the only man alive who still remembers my father as an infant. When Fred first saw my father, he was twelve [years/months] old. Who was twelve [years/months] old? Answers: Fred/my father.
In July, Kamtchatka declared war on Yakutsk. Since Yakutsk's army was much better equipped and ten times larger, they were [victorious/defeated] within weeks. Who was [victorious/defeated]Answers:  Yakutsk/Kamchatka.
Elizabeth moved her company from Sparta to Troy to save money on taxes; the taxes are much [higher/lower] there. Where are the taxes [higher/lower]? Answers: In Sparta/In Troy
Esther figures that she will save shipping costs if she builds her factory in Springfield instead of Franklin, because [most/none] of her customers live there. In which town do [most/none] of Esther's customers live? Answers: Springfield/Franklin.
Look! There is a [shark/minnow] swimming right below that duck! It had better get away to safety fast! What needs to get away to safety? Answer Pair A: The shark/The duck. Answer Pair B: The minnow/the duck.
There are too many deer in the park, so the park service brought in a small pack of wolves. The population should [increase/decrease] over the next few years. Which population will [increase/decrease]? Answers: The wolves/the deer.
Archaeologists have concluded that humans lived in Laputa 20,000 years ago. They hunted for [deer/evidence] on the river banks. Who hunted for [deer/evidence]? Answers: The prehistoric humans/the archaeologists.
The scientists are studying three species of fish that have recently been found living in the Indian Ocean. They [appeared/began] two years ago. Who or what [appeared/began] two years ago? Answers: The fish/the scientists.
The journalists interviewed the stars of the new movie. They were very [cooperative/persistent], so the interview lasted for a long time. Who was [cooperative/persistent]? Answers: The stars/the journalists
The police arrested all of the gang members. They were trying to [run/stop] the drug trade in the neighborhood. Who was trying to [run/stop] the drug trade? Answers: The gang/the police.
I put the cake away in the refrigerator. It has a lot of [butter/leftovers] in it. What has a lot of [butter/leftovers]? Answers: The cake/the refrigerator.
Sam broke both his ankles and he's walking with crutches. But a month or so from now they should be [better/unnecessary]. What should be [better/unnecessary]? Answers: The ankles/the crutches.
When the sponsors of the bill got to the town hall, they were surprised to find that the room was full of opponents. They were very much in the [majority/minority]. Who were in the [majority/minority]? Answers: The opponents /the sponsors.
Everyone really loved the oatmeal cookies; only a few people liked the chocolate chip cookies. Next time, we should make [more/fewer] of them. Which cookie should we make [more/fewer] of, next time? Answers: The oatmeal cookies/the chocolate  chip.
We had hoped to place copies of our newsletter on all the chairs in the auditorium, but there were simply [not enough/too many] of them. There are [too many/not enough] of what? Answers: chairs/copies of the newsletter.
I stuck a pin through a carrot. When I pulled the pin out, it [left/had] a hole. What [left/had] a hole? Answers: The pin/the carrot. 
I couldn't find a spoon, so I tried using a pen to stir my coffee. But that turned out to be a bad idea, because it got full of [ink/coffee]. What got full of [ink/coffee]? Answers:The coffee/the pen.
Steve follows Fred's example in everything. He [admires/influences] him hugely. Who [admires/influences] whom? Answers: Steve admires Fred/Fred influences  Steve.
The table won't fit through the doorway because it is too [wide/narrow]. What is too [wide/narrow]? Answers: The table/the doorway.
Grace was happy to trade me her sweater for my jacket. She thinks it looks [great/dowdy] on her. What looks [great/dowdy] on Grace? Answers: The jacket/the sweater.
Bill thinks that calling attention to himself was rude [to/of] Bert. Who called attention to himself? Answers: Bill/Bert.
John [hired/hired himself out to] Bill to take care of him. Who is taking care of whom? Answers: Bill is taking care of John/John is taking care of  Bill.
John [promised/ordered] Bill to leave, so an hour later he left. Who left? Answers: John/Bill.
Sam Goodman's biography of the Spartan general Xenophanes conveys a vivid sense of the difficulties he faced in his [childhood/research]. Who faced difficulties? Answers: Xenophanes/Sam.
Emma's mother had died long ago, and her [place/education] had been [taken/managed] by an excellent woman as governess. Whose [place/education] had been [taken/managed]? Answers: Emma's mother/Emma.
Jane knocked on Susan's door but she did not [answer/get an answer]. Who did not [answer/get an answer]? Answers: Susan/Jane
Joe paid the detective after he [received/delivered] the final report on the case. Who [received/delivered] the final report? Answers: Joe/the detective.
Beth didn't get angry with Sally, who had cut her off, because she stopped and [counted to ten/apologized]. Who [counted to ten/apologized]? Answers: Beth/Sally
Jim signaled the barman and gestured toward his [empty glass/bathroom key]. Whose [empty glass/bathroom key]? Answers: Jim/the barman.
Dan took the rear seat while Bill claimed the front because his "Dibs!" was [quicker/slow]. Whose "Dibs" was [quicker/slow]? Answers: Bill/Dan
Tom said "Check" to Ralph as he [took/moved] his bishop. Whose bishop did Tom [take/move]? Answers:  Ralph's /Tom's
As Andrea in the crop duster passed over Susan, she could see the landing [strip/gear]. Who could see the landing [strip/gear]? Answers: Andrea/Susan
Tom gave Ralph a lift to school so he wouldn't have to [walk/drive alone]. Who wouldn't have to [walk/drive alone]? Answers: Ralph/Tom
Bill passed the half-empty plate to John because he was [full/hungry]. Who was [full/hungry]? Answers: Bill/John
Bill passed the gameboy to John because his turn was [over/next]. Whose turn was [over/next]? Answers: Bill/John
The man lifted the boy onto his [bunk bed/shoulders]. Whose [bunk bed/shoulders]? Answers: The boy's/the man's. 
Patting/Stretching her back, the woman smiled at the girl. Whose back did the woman [pat/stretch]? Answers: The girl's/ the woman's
Billy cried because Toby wouldn't [share/accept] his toy. Who owned the toy? Answers: Toby/Billy
Lily spoke to Donna, breaking her [concentration/silence]. Whose [concentration/silence]? Answers: Donna/ Lily
When Tommy dropped his ice cream, Timmy giggled, so father gave him a [stern/sympathetic] look. Who got the look from father? Answers: Timmy/Tommy
As Ollie carried Tommy up the long winding steps, his legs [dangled/ached]. Whose legs [dangled/ached]? Answers: Tommy/Ollie
The father carried the sleeping boy in his [arms/bassinet]. Whose [arms/bassinet]? Answers: The father/the boy
The woman held the girl against her [chest/will]. Whose [chest/will]? Answers: The woman's/the girl's
Pam's parents came home and found her having sex with her boyfriend, Paul. They were [embarrassed/furious] about it. Who were [embarrassed/furious]? Answers: Pam and Paul/Pam's parents.
Dr. Adams informed Kate that she had [cancer/retired] and presented several options for future treatment. Who had [cancer/retired]? Answers: Kate/Dr. Adams
Dan had to stop Bill from toying with the injured bird. He is very [compassionate/cruel]. Who is [compassionate/cruel]? Answers: Dan/Bill
George got free tickets to the play, but he gave them to Eric [because/even though] he was [particularly/not particularly] eager to see it. Who [was/was not] eager to see the play? \\Answers:"because " \& "particularly": Eric.\\ "because" \&  "not particularly": George\\"even though"  \& "particularly":  George\\"even though" \&  "not particularly": Eric
Jane gave Joan candy because she [was/wasn't] hungry. Who [was/wasn't] hungry? Answers: Joan/Jane.
I tried to paint a picture of an orchard, with lemons in the lemon trees, but they came out looking more like [light bulbs /telephone poles]. What looked like [light bulbs/telephone poles]? Answers: The lemons/the trees.
James asked Robert for a favor but he [refused/was refused]. Who [refused/was refused]? Answers: Robert/James
Kirilov ceded the presidency to Shatov because he was [more/less] popular. Who was [more/less] popular? Answers: Shatov/Kirilov
Emma did not pass the ball to Janie although she [was open/saw that she was open]. Who [was open/saw that the other player was open]? Answers: Janie/Emma
Joe saw his brother skiing on TV last night but the fool didn't [recognize him/have a coat on] Who is the fool? Answers: Joe/Joe's brother.
I put the [heavy book/butterfly wing] on the table and it broke. What broke? Answer Pair A: The table/The book Answer Pair B: The butterfly wing/The table
Madonna fired her trainer because she [slept with/couldn't stand] her boyfriend. Who [slept with/couldn't stand] whose boyfriend? Answer: The trainer slept with Madonna 's boyfriend/Madonna couldn't stand the  train er's boyfriend.
Carol believed that Rebecca [suspected/regretted] that she had stolen the watch. Who is suspected of stealing the watch?/Who stole the watch? Answer: Carol/Rebecca
This book introduced Shakespeare to [Ovid/Goethe]; it was a major influence on his writing. Whose writing was influenced? Answer: Shakespeare/Goethe
This book introduced Shakespeare to [Ovid/Goethe]; it was a fine selection of his writing. A fine selection of whose writing? Answer: Ovid/ Shakespeare
Alice looked for her friend Jade in the crowd. Since she always [has good luck/wears a red turban], Alice spotted her quickly. Who always [has good luck/wears a red turban]Answer: Alice/Jade
During a game of tag, Ethan [chased/ran from] Luke because he was "it". Who was "it"? Answer: Ethan/Luke
At the Loebner competition the judges couldn't figure out which respondents were the chatbots because they were so [advanced/stupid]. Who were so [advanced/stupid]? Answer: the chatbots/the judges.
The user changed his password from "GrWQWu8JyC" to "willow-towered Canopy Huntertropic wrestles" as it was easy to [remember/forget]. What was easy to [remember/forget]? Answer: the password  "GrWQWu8JyC"/ the password  " willow-towered Canopy Huntertropic wrestles") \end{foo}

%TODO add table with 150 rows and 5 columns; for Annotator 1 add red mark for Annotator 2 add blue mark

